Assignment #1 by Jaime de Mora

First we're going to upload the data

```{r, echo=TRUE}
activity <- read.csv('activity.csv', stringsAsFactors = FALSE)
str(activity)
activity$date <- as.Date(activity$date)
```

Let's count the number of steps

```{r, echo=TRUE}
activity_clean <- activity[which(!is.na(activity$steps)),]
perday <- tapply(activity_clean$steps, activity_clean$date, sum)
mean(perday)
median(perday)
hist(perday, 20)
```

### Average Daily Activity Pattern

```{r, echo=TRUE}
daily_activity <- tapply(activity_clean$steps, activity_clean$interval, sum)
plot(y=daily_activity, x=names(daily_activity), type="l")
```

And the 5 minute inverval with a highest number of steps is:

```{r, echo=TRUE}
daily_activity[daily_activity==max(daily_activity)]
```

### Inputting missing values
```{r, echo=TRUE}
sum(is.na(activity$steps))

act_new <- activity
act_new$steps[is.na(act_new$steps)] <- mean(activity$steps, na.rm=TRUE)

sum(is.na(act_new))

sum_steps <- aggregate(act_new$steps, by=list(act_new$date),FUN=sum,na.rm=TRUE)

par(mfrow=c(1,2))
hist(perday, 20, main ="Total Number of Steps")
hist(sum_steps$x, 20, main = "Total Number of Steps (with no NAs)")
```

Now let's calculate the difference of mean and median between the original and filled in dataset

```{r}
mean(sum_steps$x)
median(sum_steps$x)

mean(perday)
median(perday)
```

## Difference between weekdays and weekends

Let's see the difference in terms of activity between both categories

```{r}
act_new$wd<-weekdays(act_new$date)
act_new$fwd<- as.factor(c("weekend", "weekday"))
act_new[act_new$wd == "Sunday" | act_new$wd == "Saturday" ,5]<- factor("weekend")
act_new[!(act_new$wd == "Sunday" | act_new$wd == "Saturday"),5 ]<- factor("weekday")
```

```{r}
act_new_we <- subset(act_new, fwd == "weekend") 
act_new_wd <- subset(act_new, fwd == "weekday") 
dailyact_we<-tapply(act_new_we$steps, act_new_we$interval, mean)
dailyact_wd<-tapply(act_new_wd$steps, act_new_wd$interval, mean)
par(mfrow=c(2,1))
plot(y = dailyact_wd, x = names(dailyact_wd), type = "l", xlab = "5-Minute Interval", 
     main = "Daily Activity Pattern on Weekdays", ylab = "Average number of steps", 
     ylim =c(0, 250))
plot(y = dailyact_we, x = names(dailyact_we), type = "l", xlab = "5-Minute Interval", 
     main = "Daily Activity Pattern on Weekends", ylab = "Average number of steps", 
     ylim =c(0, 250))
```


